Toward dynamic models of combat or lack thereof in animal mating

### 2016-01-14 ms.tex
info re: SSA -> ms.tex

\subsection{Event Algorithm}
See Fig. \ref{fig:events}. Population state generates events, events are either:
\begin{enumerate}
    \item A new individual x has matured and entered the pool (based off of a trait(?))
    \item Discovery event wherin both a nest RR (repoductive resource) and an individual x are drawn from a pool, the metabolic costs of searching are deducted from the time differences between events, that nest is either:
    \begin{enumerate}
        \item un-occupied: in which x takes ownership of RR.
        \item occupied by x' in which a constest occurs (see fig 2)
    \end{enumerate}
\end{enumerate}
After the contest Energy costs are deducted from both the winner and the loser.
The winner also has a chance to abandon the RR (based off a trait).
If a death occurs (Energy(x) less than 0) then x is removed from the individual pool.

@@

\begin{enumerate}
    \item Display 1
        Outcomes:
        \begin{itemize}
            \item $x_{atk}$ escalates: 
                $Pr(\rm{escalation}) =  logit^{-1}(a_{atk} \cdot m_{atk} - m_{def})$
                or leaves.
            \item $x_{def}$ escalates:
                $Pr(\rm{escalation}) =  logit^{-1}(a_{def} \cdot m_{def} - m_{atk})$ 
                or leaves.
            \item if the attacker leaves the defender keeps the nest
            \item if the defender leaves the attacker keeps the nest
            \item the attacker is evaluated first
            \item if they both escalate then the next stage occurs
        \end{itemize}
    \item Display 2:
        similar to stage 1, this could involve the $R$ value of the nest, or include the oponents aggression levels or energy reseves(?).
    \item Fight
\end{enumerate}
The cost of the fighting stage is much greater than the cost of the display stage.

In the display phases the probability of escalation is dependent on the visible traits of x and x'
The rate of events increases as time t approaches t1

>>>>

\subsection{Event Algorithm}
See Fig. \ref{fig:events}. Population state generates events, events are either:
\begin{enumerate}
    \item A new individual x has matured and entered the pool (based off of a trait(?))
    \item Discovery event wherin both a nest RR (repoductive resource) and an individual x are drawn from a pool, the metabolic costs of searching are deducted from the time differences between events, that nest is either:
    \begin{enumerate}
        \item un-occupied: in which x takes ownership of RR.
        \item occupied by x' in which a constest occurs (see fig 2)
    \end{enumerate}
\end{enumerate}

In the SSA algorithm \citep{Gillespie-1976} there are 6 different \"species\", representing different states:
\begin{enumerate}
    \item $S_1 = $ immature male
    \item $S_2 = $ mature searching male
    \item $S_3 = $ unoccupied nest
    \item $S_4 = $ occupied nest
    \item $S_5 = $ recently defeated male
    \item $S_6 = $ recently changed nest
\end{enumerate}

these species have $R_\mu$ different interactions
\begin{table}[h!]
    \caption{state changes}
    \centering
    \begin{tabular}{c | c | c | c | l }
        \hline
        Reaction num & reactants  & & products & Description\\
        \hline
        \hline
            $R_1$       &   $S_1$       & $--c_1-->$       &   $ S_2$      & maturation\\
            $R_2$       &   $S_2 + S_3$ & $--c_2-->$      &   $S_4 $      & occupation\\
            $R_3$       &   $S_2 + S_4$ & $--c_3-->$      &   $S_4 + S_5$ & contest\\
            $R_4$       &   $S_5$       & $--c_4-->$      &   $S_2$       & recovery\\
            $R_5$       &   $S_2 + S_4$ & $--c_5-->$      &   $S_4$       & contest with death\\
            $R_6$       &   $S_4$       & $--c_6-->$      &   $S_2 + S_3$ & abandon event\\
            $R_7$       &   $S_1$       & $--c_7-->$      &   $0$         & metab0lic / predation event\\
            $R_8$       &   $S_2$       & $--c_8-->$      &   $0$         & predation event\\
            $R_9$       &   $S_4$       & $--c_9-->$      &   $S_3$       & metab0lic / predation event\\
            $R_{10}$    &   $S_6$       & $--c_{10}-->$   &   $S_4$       & nest handover\\
        \hline
    \end{tabular}
\end{table}

$c_n$ is the stochatic reaction constant

@@

$m$ is mass
$a$ is aggression trait
\begin{enumerate}
    \item Display 1
        Outcomes:
        \begin{itemize}
            \item $x_{atk}$ escalates: 
                $Pr(\rm{escalation}) =  logit^{-1}(a_{atk} \cdot m_{atk} - m_{def})$
                or leaves.
            \item $x_{def}$ escalates:
                $Pr(\rm{escalation}) =  logit^{-1}(a_{def} \cdot m_{def} - m_{atk})$ 
                or leaves.
            \item if the attacker leaves the defender keeps the nest
            \item if the defender leaves the attacker keeps the nest
            \item the attacker is evaluated first
            \item if they both escalate then the next stage occurs
        \end{itemize}
    \item Display 2:
        similar to stage 1, this could involve the $R$ value of the nest, or include the oponents aggression levels or energy reseves(?).
    \item Fight
        So far I have something like
        \begin{itemize}
            \item $x_{def}$ wins:
            $Pr(\rm{def}) = logit{-1}(m_{def} - m_{atk})$
        \end{itemize}
\end{enumerate}
The cost of the fighting stage is much greater than the cost of the display stage.

In the display phases the probability of escalation is dependent on the visible traits of x and x'

After the contest Energy costs are deducted from both the winner and the loser.
The winner also has a chance to abandon the RR (based off a trait).
If a death occurs (Energy(x) less than 0) then x is removed from the individual pool.
